Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-11-30 paper-ApJ/ms.tex
Add paper-ApJ

% region preamble

\documentclass[fleqn,usenatbib]{mnras}

\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% endregion

% region title
%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Stellar Bars and Gas]{Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down}

\author[A. Beane et al.]{Angus Beane,$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu (AB)}
Lars Hernquist,$^{1}$
Elena~D'Onghia,$^{2,3}$
Federico~Marinacci,$^{4}$
Charlie Conroy,$^{1}$
Jia~Qi,$^{5}$\newauthor
Laura~V.~Sales,$^{6}$
Paul~Torrey,$^{5}$
Mark~Vogelsberger$^{7}$
\\
% List of institutions
$^{1}$Center for Astrophysics $|$ Harvard \& Smithsonian,  Cambridge, MA, USA\\
$^{2}$Department of Physics, University of Wisconsin-Madison, Madison, WI, USA\\
$^{3}$Department of Astronomy, University of Wisconsin-Madison, Madison, WI, USA\\
$^{4}$Department of Physics \& Astronomy `Augusto Righi', University of Bologna, Bologna, Italy\\
$^{5}$Department of Astronomy, University of Florida, Gainesville, FL, USA\\
$^{6}$Department of Physics \& Astronomy, University of California, Riverside, CA, USA\\
$^{7}$Department of Physics, Massachusetts Institute of Technology, Cambridge, MA, USA\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2022}

% endregion

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
Elongated bar-like features are ubiquitous in galaxies, occurring at the centers
of approximately two-thirds of spiral disks.  Due to gravitational interactions
between the bar and the other components of galaxies, it is expected that
angular momentum and matter will redistribute over long (Gyr) timescales in
barred galaxies. Previous work ignoring the gas phase of galaxies has
conclusively demonstrated that bars should slow their rotation over time due to
their interaction with dark matter halos. We have performed a simulation of a
Milky Way-like galactic disk hosting a strong bar which includes a
state-of-the-art model of the interstellar medium and a live dark matter halo.
In this simulation the bar pattern does not slow down over time, and instead
remains at a stable, constant rate of rotation. This behavior has been observed
in previous simulations using more simplified models for the interstellar gas,
but the apparent lack of secular evolution has remained unexplained. We propose
that the gas phase of the disk and the dark matter halo act in concert to
stabilize the bar pattern speed and prevent the bar from slowing down or
speeding up. We find that in a Milky Way-like disk, a gas fraction of only about
5\% is necessary for this mechanism to operate. Our result naturally explains
why nearly all observed bars rotate rapidly and is especially relevant for our
understanding of how the Milky Way arrived at its present state.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
galaxies: bar - galaxies: disc - galaxies: evolution - galaxies: kinematics and
dynamics
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

@@

It is more difficult to reconcile numerical simulations with the observed
pattern speeds of extragalactic bars. Currently, the best technique for
measuring the pattern speeds of individual galaxies is the Tremaine-Weinberg
method \citep{1984ApJ...282L...5T, 2011MSAIS..18...23C}. This approach has
recently been applied to samples of galaxies from the MaNGA survey
\citep{2019MNRAS.482.1733G, 2020MNRAS.491.3655G}. These studies confirm
what was found in earlier works, that nearly all extragalactic bars are fast
rotators (i.e., they rotate close to their maximum rotation rate)

@@

% \subsection{Figures and tables}

% Figures and tables should be placed at logical positions in the text. Don't
% worry about the exact layout, which will be handled by the publishers.

% Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
% e.g. Table~\ref{tab:example_table}.

% % Example figure
% \begin{figure}
% 	% To include a figure from a file named example.*
% 	% Allowable file formats are eps or ps if compiling using latex
% 	% or pdf, png, jpg if compiling using pdflatex
% 	\includegraphics[width=\columnwidth]{example}
%     \caption{This is an example figure. Captions appear below each figure.
% 	Give enough detail for the reader to understand what they're looking at,
% 	but leave detailed discussion to the main body of the text.}
%     \label{fig:example_figure}
% \end{figure}

% % Example table
% \begin{table}
% 	\centering
% 	\caption{This is an example table. Captions appear above each table.
% 	Remember to define the quantities, symbols and units used.}
% 	\label{tab:example_table}
% 	\begin{tabular}{lccr} % four columns, alignment for each
% 		\hline
% 		A & B & C & D\\
% 		\hline
% 		1 & 2 & 3 & 4\\
% 		2 & 4 & 6 & 8\\
% 		3 & 5 & 7 & 9\\
% 		\hline
% 	\end{tabular}
% \end{table}

@@

We allow the bar in this model to rotate as a solid body. However, we crucially
allow the pattern speed of the bar to freely change with time in accordance with
the torque exerted on the dark matter halo by the bar. In particular, we
subtract the $z$-component of this torque divided by the moment of inertia of
the bar from the pattern speed at each timestep. Since the radius of corotation
\RCR{} is a parameter in the bar model from \citet{2022MNRAS.513..768C}, we
allow the moment of inertia of the bar to vary with ${\RCR}^2$. To be more
precise, we allow
\begin{equation}
I = \frac{I_6}{10^{10} \Msun (\kms)^2} \left( \frac{\RCR}{6\,\textrm{kpc}} \right)^2\textrm{,}
\end{equation}
where $I_6$ is a free parameter chosen by the user. We found that allowing
$I_6=8$ is a good approximation to our fiducial disk model. In code units, the
moment of inertia of the SMUGGLE bar (i.e., the particles classified as being in
the bar) is about $2$. This is a factor of $4$ smaller than our fiducial value
of $I_6=8$, but this is probably due to the fact that the bar does not really
rotate as a solid body.

@@

We next take the $\tau_{\textrm{gas}}=0$ and $20$ cases from Fig.~\ref{fig:sam}
and plot the torque evolution. This result, given in Fig.~\ref{fig:sam-torque},
is comparable to the lower panel of Fig.~\ref{fig:prop}. We find that the
$\tau_{\textrm{gas}}=0$ case compares favorably to the \Nbody{} case described
in previous sections. The bar exerts a steady negative torque in this case (blue
line). When a gas torque is included (orange lines), we find that the halo's
torque becomes much weaker, similar to what we found in the SMUGGLE case. The
gas applies a steady positive torque by construction. Therefore, the exhaustion
process is reproduced in our simple semi-analytic model.

@@

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F}. However,
the pattern speeds of bars in both cosmological simulations and the real
universe can be affected by environmental processes not included in our
simulation -- e.g., satellite infall \citep{2011Natur.477..301P}, non-sphericity
\citep{2013MNRAS.429.1949A}, rotation in the dark matter halo
\citep{2013MNRAS.434.1287S, 2014ApJ...783L..18L, 2018MNRAS.476.1331C,
2019MNRAS.488.5788C}, or perhaps even the gaseous circumgalactic medium.
Naturally, extending our present work to account for such effects is a crucial
next step in understanding the formation and evolution of galactic bars. We are
presently engaged in such an exploration.

@@

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which have been gas-poor for
extended periods of time to be rotating very slowly. We therefore predict that
observations which target such galaxies (e.g., lenticular barred galaxies
\citep{2009ARAA..47..159B}) would find slowly rotating bars.\footnote{This does
not mean that we predict \textit{all} gas-poor galaxies should be slowly
rotating. Indeed, they would need to be gas-deficient for several $\textrm{Gyr}$
before they would be classified as slow rotators.} There does exist one example
of a galaxy which is known to be a slow rotator -- the low surface brightness
galaxy UGC 628 \citep{2009AA...499L..25C}. This galaxy has been studied in
detail by \citet{2016MNRAS.463.1751C}, who note that it indeed has a low gas
fraction for galaxies of its type. We predict a general trend that bars in
gas-rich spiral galaxies should rotate quickly while some bars in gas-poor
spiral galaxies should rotate slowly.
https://github.com/gusbeane/gasbar
\section*{Acknowledgements}
We would like to thank Greg~L. Bryan, Neal~J. Evans, Drummond~B. Fielding, Keith
Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson, Kathryn~V. Johnston,
Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro, Joshua~S. Speagle,
Martin~D. Weinberg, and Yanfei Zou for helpful discussions. A.B. would like to
thank Todd Phillips for helpful discussions. Some computations in this paper
were run on the FASRC Cannon cluster supported by the FAS Division of Science
Research Computing Group at Harvard University. Resources supporting this work
were also provided by the NASA High-End Computing (HEC) Program through the NASA
Advanced Supercomputing (NAS) Division at Ames Research Center. This research
has made use of the Spanish Virtual Observatory (https://svo.cab.inta-csic.es)
project funded by MCIN/AEI/10.13039/501100011033/ through grant
PID2020-112949GB-I00. A.B. was supported by the Future Investigators in NASA
Earth and Space Science and Technology (FINESST) award number 80NSSC20K1536
during the completion of this work. E.D. was partially supported by HST grants
HST-AR-16363.001 and HST-AR-16602.006-A and by NASA Award NASA 80NSSC22K0761.
J.Q. acknowledges support from NSF grant AST-2008490. L.V.S. is grateful for
financial support from NASA ATP 80NSSC20K0566, NSF AST 1817233 and NSF CAREER
1945310 grants. P.T. acknowledges support from NSF grant AST-1909933,
AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges support through
NASA ATP 19-ATP19-0019, 19-ATP19-0020, 19-ATP19-0167, and NSF grants
AST-1814053, AST-1814259, AST-1909831, AST-2007355 and AST-2107724.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}
A git repository containing all analysis scripts and notebooks is available at
\url{https://github.com/gusbeane/gasbar}. Snapshots at a $500\,\Myr$ cadence, as
well as the initial conditions, are available at
\url{https://drive.google.com/drive/folders/1nZF7mZ98T0QPc2pt7CVCUUdQAm7Q9nK-?usp=sharing}.
Snapshots at a higher cadence are available upon request without expectation of
coauthorship.

We made use of the following software packages in {\sc Python} \citep{Python}:
{\sc agama} \url{https://github.com/GalacticDynamics-Oxford/Agama}, {\sc
astropy} \citep{astropy:2013, astropy:2018}, {\sc h5py}
\url{http://www.h5py.org/}, {\sc inspector\_gadget}
\url{https://bitbucket.org/abauer/inspector_gadget/}, {\sc joblib}
\url{https://joblib.readthedocs.io/en/latest/}, {\sc matplotlib}
\citep{Hunter:2007}, {\sc numba} \citep{Lam:2015bfh}, {\sc numpy}
\citep{harris2020array}, {\sc scipy} \citep{2020SciPy-NMeth}, {\sc tqdm}
\url{https://tqdm.github.io/}.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{ref} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}

@@

% End of mnras_template.tex

>>>>

%% Beginning of file 'sample631.tex'
%%
%% Modified 2021 March
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
\documentclass[twocolumn,linenumbers]{aastex631}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be invoked like this:
%%
%% \documentclass[arguments]{aastex631}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Supresses an abstract. Originally for RNAAS manuscripts 
%%                but now that abstracts are required this is obsolete for
%%                AAS Journals. Authors might need it for other reasons. DO NOT
%%                use \begin{abstract} and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%   tighten      : Makes baselineskip slightly smaller, only works with 
%%                  the twocolumn substyle.
%%   times        : uses times font instead of the default
%%   linenumbers  : turn on lineno package.
%%   trackchanges : required to see the revision mark up and print its output
%%   longauthor   : Do not use the more compressed footnote style (default) for 
%%                  the author/collaboration/affiliations. Instead print all
%%                  affiliation information after each name. Creates a much 
%%                  longer author list but may be desirable for short 
%%                  author papers.
%% twocolappendix : make 2 column appendix.
%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
%%                  for dual anonymous review.
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex631}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
%% to improve the accessibility of the compiled pdf file.
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%

@@

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{March 1, 2021}
%\revised{April 1, 2021}
%\accepted{\today}

\shorttitle{Stellar Bars and Gas}
\shortauthors{Beane et al.}

\graphicspath{{./}{figures/}}

\begin{document}

\title{Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.31 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affiliations. The change was necessary to implement 
%% auto-indexing of affiliations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% argument which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
%% present or in the LaTeX pathway, the OrcID icon will appear next to
%% the authors name.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.31 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.31 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

%\correspondingauthor{August Muench}
%\email{greg.schwarz@aas.org, gus.muench@aas.org}

\author{Angus Beane}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian,  Cambridge, MA, USA}

\author{Lars Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian,  Cambridge, MA, USA}

\author{Elena D'Onghia}
\affiliation{Department of Physics, University of Wisconsin-Madison, Madison, WI, USA}
\affiliation{Department of Astronomy, University of Wisconsin-Madison, Madison, WI, USA}

\author{Federico Marinacci}
\affiliation{Department of Physics \& Astronomy `Augusto Righi', University of Bologna, Bologna, Italy}

\author{Charlie Conroy}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian,  Cambridge, MA, USA}

\author{Jia Qi}
\affiliation{Department of Astronomy, University of Florida, Gainesville, FL, USA}

\author{Laura V. Sales}
\affiliation{Department of Physics \& Astronomy, University of California, Riverside, CA, USA}

\author{Paul Torrey}
\affiliation{Department of Astronomy, University of Florida, Gainesville, FL, USA}

\author{Mark Vogelsberger}
\affiliation{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA, USA}

\begin{abstract}

  Elongated bar-like features are ubiquitous in galaxies, occurring at the
  centers of approximately two-thirds of spiral disks.  Due to gravitational
  interactions between the bar and the other components of galaxies, it is
  expected that angular momentum and matter will redistribute over long (Gyr)
  timescales in barred galaxies. Previous work ignoring the gas phase of
  galaxies has conclusively demonstrated that bars should slow their rotation
  over time due to their interaction with dark matter halos. We have performed a
  simulation of a Milky Way-like galactic disk hosting a strong bar which
  includes a state-of-the-art model of the interstellar medium and a live dark
  matter halo. In this simulation the bar pattern does not slow down over time,
  and instead remains at a stable, constant rate of rotation. This behavior has
  been observed in previous simulations using more simplified models for the
  interstellar gas, but the apparent lack of secular evolution has remained
  unexplained. We propose that the gas phase of the disk and the dark matter
  halo act in concert to stabilize the bar pattern speed and prevent the bar
  from slowing down or speeding up. We find that in a Milky Way-like disk, a gas
  fraction of only about 5\% is necessary for this mechanism to operate. Our
  result naturally explains why nearly all observed bars rotate rapidly and is
  especially relevant for our understanding of how the Milky Way arrived at its
  present state.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% The AAS Journals now uses Unified Astronomy Thesaurus concepts:
%% https://astrothesaurus.org
%% You will be asked to selected these concepts during the submission process
%% but this old "keyword" functionality is maintained in case authors want
%% to include these concepts in their preprints.
\keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

@@

It is more difficult to reconcile numerical simulations with the observed
pattern speeds of extragalactic bars. Currently, the best technique for
measuring the pattern speeds of individual galaxies is the Tremaine-Weinberg
method \citep{1984ApJ...282L...5T, 2011MSAIS..18...23C}. This approach has
recently been applied to samples of galaxies from the MaNGA survey
\citep{2019MNRAS.482.1733G, 2020MNRAS.491.3655G}. These studies confirm
what was found in earlier works, that nearly all extragalactic bars are fast
rotators (i.e., they rotate close to their maximum rotation rate).

@@

@@

We allow the bar in this model to rotate as a solid body. However, we crucially
allow the pattern speed of the bar to freely change with time in accordance with
the torque exerted on the dark matter halo by the bar. In particular, we
subtract the $z$-component of this torque divided by the moment of inertia of
the bar from the pattern speed at each timestep. Since the radius of corotation
\RCR{} is a parameter in the bar model from \citet{2022MNRAS.513..768C}, we
allow the moment of inertia of the bar to vary with ${\RCR}^2$. To be more
precise, we allow
\begin{equation}
I = \frac{I_6}{10^{10} \Msun (\kms)^2} \left( \frac{\RCR}{6\,\textrm{kpc}} \right)^2\textrm{,}
\end{equation}
where $I_6$ is a free parameter chosen by the user. We found that allowing
$I_6=8$ is a good approximation to our fiducial disk model. In code units, the
moment of inertia of the SMUGGLE bar (i.e., the particles classified as being in
the bar) is about $2$. This is a factor of $4$ smaller than our fiducial value
of $I_6=8$, but this is probably due either to the fact that the bar does not
really rotate as a solid body or that resonantly captured stars contribute to
the real bar's effective moment of inertia \citep{1985MNRAS.213..451W}.

@@

We next take the $\tau_{\textrm{gas}}=0$ and $20$ cases from Fig.~\ref{fig:sam}
and plot the halo torque evolution. This result, given in Fig.~\ref{fig:sam-torque},
is comparable to the lower panel of Fig.~\ref{fig:prop}. We find that the
$\tau_{\textrm{gas}}=0$ case compares favorably to the \Nbody{} case described
in previous sections. The bar exerts a steady negative torque in this case (blue
line). When a gas torque is included (orange lines), we find that the halo's
torque becomes much weaker, similar to what we found in the SMUGGLE case. The
gas applies a steady positive torque by construction. Therefore, the exhaustion
process is reproduced in our simple semi-analytic model.

@@

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F,
2022ApJ...940...61F}. However, the pattern speeds of bars in both cosmological
simulations and the real universe can be affected by environmental processes not
included in our simulation -- e.g., satellite infall
\citep{2011Natur.477..301P}, non-sphericity \citep{2013MNRAS.429.1949A},
rotation in the dark matter halo \citep{2013MNRAS.434.1287S,
2014ApJ...783L..18L, 2018MNRAS.476.1331C, 2019MNRAS.488.5788C}, or perhaps even
the gaseous circumgalactic medium. Naturally, extending our present work to
account for such effects is a crucial next step in understanding the formation
and evolution of galactic bars. We are presently engaged in such an exploration.
We note that \citet{2022ApJ...940...61F} argue that bars in the TNG50 simulation
are too short rather than too slow.

@@

We found that below a certain gas fraction, bars should still be able to slow
down. Therefore, we expect barred spiral galaxies which have been gas-poor for
extended periods of time to be rotating very slowly. We therefore predict that
observations which target such galaxies (e.g., lenticular barred galaxies
\citep{2009ARAA..47..159B}) would find slowly rotating bars.\footnote{This does
not mean that we predict \textit{all} gas-poor galaxies should be slowly
rotating. Indeed, they would need to be gas-deficient for several $\textrm{Gyr}$
before they would be classified as slow rotators.} There does exist one example
of a galaxy which is known to be a slow rotator -- the low surface brightness
galaxy UGC 628 \citep{2009AA...499L..25C}. This galaxy has been studied in
detail by \citet{2016MNRAS.463.1751C}, who note that it indeed has a low gas
fraction for galaxies of its type. We predict a general trend that bars in
gas-rich spiral galaxies should rotate quickly while some bars in gas-poor
spiral galaxies should rotate slowly.

\begin{acknowledgments}
  We would like to thank Greg~L. Bryan, Neal~J. Evans, Drummond~B. Fielding, Keith
  Hawkins, Jason~A.~S. Hunt, Sarah~M.~R. Jeffreson, Kathryn~V. Johnston,
  Peter~M.~W. Kalberla, Jürgen Kerp, Julio~F. Navarro, Joshua~S. Speagle,
  Martin~D. Weinberg, and Yanfei Zou for helpful discussions. A.B. would like to
  thank Todd Phillips for helpful discussions. Some computations in this paper
  were run on the FASRC Cannon cluster supported by the FAS Division of Science
  Research Computing Group at Harvard University. Resources supporting this work
  were also provided by the NASA High-End Computing (HEC) Program through the NASA
  Advanced Supercomputing (NAS) Division at Ames Research Center. This research
  has made use of the Spanish Virtual Observatory (https://svo.cab.inta-csic.es)
  project funded by MCIN/AEI/10.13039/501100011033/ through grant
  PID2020-112949GB-I00. A.B. was supported by the Future Investigators in NASA
  Earth and Space Science and Technology (FINESST) award number 80NSSC20K1536
  during the completion of this work. E.D. was partially supported by HST grants
  HST-AR-16363.001 and HST-AR-16602.006-A and by NASA Award NASA 80NSSC22K0761.
  J.Q. acknowledges support from NSF grant AST-2008490. L.V.S. is grateful for
  financial support from NASA ATP 80NSSC20K0566, NSF AST 1817233 and NSF CAREER
  1945310 grants. P.T. acknowledges support from NSF grant AST-1909933,
  AST-2008490, and NASA ATP Grant 80NSSC20K0502. M.V. acknowledges support through
  NASA ATP 19-ATP19-0019, 19-ATP19-0020, 19-ATP19-0167, and NSF grants
  AST-1814053, AST-1814259, AST-1909831, AST-2007355 and AST-2107724.
\end{acknowledgments}

\software{
{\sc agama} \url{https://github.com/GalacticDynamics-Oxford/Agama}, {\sc
astropy} \citep{astropy:2013, astropy:2018}, {\sc h5py}
\url{http://www.h5py.org/}, {\sc inspector\_gadget}
\url{https://bitbucket.org/abauer/inspector_gadget/}, {\sc joblib}
\url{https://joblib.readthedocs.io/en/latest/}, {\sc matplotlib}
\citep{Hunter:2007}, {\sc numba} \citep{Lam:2015bfh}, {\sc numpy}
\citep{harris2020array}, {\sc scipy} \citep{2020SciPy-NMeth}, {\sc tqdm}
\url{https://tqdm.github.io/}
          }

@@

%% For this sample we use BibTeX plus aasjournals.bst to generate the
%% the bibliography. The sample631.bib file was populated from ADS. To
%% get the citations to show in the compiled file do the following:
%%
%% pdflatex sample631.tex
%% bibtext sample631
%% pdflatex sample631.tex
%% pdflatex sample631.tex

\bibliography{ref}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

@@

% End of file `sample631.tex'.
